Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-14 paper/paper.tex
nudge

Using the closed-loop control system benchmarks described in Section~\ref{experimental-setup}, 
the experimental evaluation of the present approach aims to answer two research questions:
%
\begin{enumerate}

@@

\caption{Experimental results\label{tab:results}}
\end{table}
%---------------------------------

The median runtime for our benchmark set is $197$\,s, implying that half of
the controllers can be synthesised in less than $5$ minutes using our
present approach.  Overall, the average synthesis time amounts to
approximately $30$ minutes.  With respect to RQ2 we consider these times
short enough to be of practical use to control engineers.  Regarding RQ1 we
further conclude that the approach using a two-stage verification engine is
able to synthesise stable controllers in the $12$ out of $15$ benchmarks,
and can be complemented using the one-stage engine for $2$ additional
benchmarks, where the inductive conjectures fail.  Both verification engines
together enabled controller synthesis for $14$ out of $15$ benchmarks.  For
the $1$ remaining benchmark our approach failed to synthesise a stable
controller in the requested time limits.  This can be addressed by either
increasing the fixed point word widths considered or using floating point
arithmetic instead.  A link to the full experimental environment, including
scripts to reproduce the results, all benchmarks and the DDSynth tool, is
provided in the
footnote.\footnote{\url{https://drive.google.com/file/d/0ByIexo3Z5N91QkhrMi1rdkZFTWc/view}}

>>>>

Using the closed-loop control system benchmarks described in
Section~\ref{experimental-setup}, our experimental evaluation aims to answer
two research questions:
%
\begin{enumerate}

@@

\caption{Experimental results obtained with \tool\label{tab:results}}
\end{table}
%---------------------------------

The median runtime for our benchmark set is $197$\,s, implying that \tool
can synthesise half of the controllers in less than $5$ minutes.  Overall,
the average synthesis time amounts to approximately $30$ minutes.  With
respect to RQ2 we consider these times short enough to be of practical use
to control engineers.  Regarding RQ1 we further conclude that the approach
using a two-stage verification engine is able to synthesise stable
controllers in the $12$ out of $15$ benchmarks, and can be complemented
using the one-stage engine for $2$ additional benchmarks, where the
inductive conjectures fail.  Both verification engines together enabled
controller synthesis for $14$ out of $15$ benchmarks.  For the $1$ remaining
benchmark our approach failed to synthesise a stable controller in the
requested time limits.  This can be addressed by either increasing the fixed
point word widths considered or using floating point arithmetic instead. 
A~link to the full experimental environment, including scripts to reproduce
the results, all benchmarks and the \tool tool, is provided in the
footnote.\footnote{\url{https://drive.google.com/file/d/0ByIexo3Z5N91QkhrMi1rdkZFTWc/view}}
